---
title: "R Notebook"
output: html_notebook
---

##### **Chapter 13**

###### **13.1**

* Multiple tables of data are called relational data

* Three families of verbs designed to work with relational data:
    + Mutating joins, which add new variables to one data frame from matching observations in another.
    + Filtering joins, which filter observations from one data frame based on whether or not they match an observation in the other table.
    + Set operations, which treat observations as if they were set elements.

```{r, include=FALSE}
library(tidyverse)
install.packages("nycflights13")
library(nycflights13)
```


###### **13.2**

* For nycflights13:
    + flights connects to planes via a single variable, tailnum.
    + flights connects to airlines through the carrier variable.
    + flights connects to airports in two ways: via the origin and dest variables.
    + flights connects to weather via origin (the location), and year, month, day and hour (the time).

###### **13.3**

* There are two types of keys:
    + A primary key uniquely identifies an observation in its own table. For example, planes$tailnum is a primary key because it uniquely identifies each plane in the planes table.
    + A foreign key uniquely identifies an observation in another table. For example, the flights$tailnum is a foreign key because it appears in the flights table where it matches each flight to a unique plane.

###### **13.4**

* A mutating join allows you to combine variables from two tables. It first matches observations by their keys, then copies across variables from one table to the other.

```{r}
x <- tribble(
  ~key, ~val_x,
     1, "x1",
     2, "x2",
     3, "x3"
)
y <- tribble(
  ~key, ~val_y,
     1, "y1",
     2, "y2",
     4, "y3"
)

x %>% 
  inner_join(y, by = "key")
left_join(x, y, by = "key")
```


###### **13.5**

* Filtering joins
    + semi_join(x, y) keeps all observations in x that have a match in y.
    + anti_join(x, y) drops all observations in x that have a match in y.

###### **13.6**

* Real data will never be clean. Problems will be expected

###### **13.7**

* Set operations (used least frequently)
    + intersect(x, y): return only observations in both x and y.
    + union(x, y): return unique observations in x and y.
    + setdiff(x, y): return observations in x, but not in y.




